Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors

### 2012-12-18 Publications/2013-IPMI/Latex/045-Experiments.tex

\paragraph{Extracted scalar features}
The target \ac{dwi} data is characterized by its distortions and its
low resolution (typically around $2.2x2.2x3mm^3$). Depending on the
posterior reconstruction methodology and the angular resolution
intended, the \ac{dwi} raw data has to be processed in order to
extract the information in a manageable manner. The properties of
the reconstructed tensors and derived scalar maps have been
studied by \cite{ennis_orthogonal_2006}. Based on their
findings, the proposed energy model adapts to the \ac{fa} and \ac{md}
for their properties. Whereas \ac{fa} describes the \emph{shape} of diffusion, 
the \ac{md} depicts the \emph{magnitude} of the process. 
There exist two main reasons to justify their choice. 
First, they are well-understood and standardized in clinical routine.
Second, together they contain most of the information that is
usually extracted from the \ac{dwi}-derived scalar maps. \\

>>>>

\paragraph{Derived scalar features}
The target \ac{dwi} data is characterized by its distortions and its
low resolution (typically around $2.2x2.2x3mm^3$). Depending on the
posterior reconstruction methodology and the angular resolution
intended, the \ac{dwi} raw data has to be processed in order to
extract the information in a manageable manner. The properties of
the reconstructed tensors and derived scalar maps have been
studied by \cite{ennis_orthogonal_2006}. Based on their
findings, the proposed energy model adapts to the \ac{fa} and \ac{md}
for their properties. Whereas \ac{fa} describes the \emph{shape} of diffusion, 
the \ac{md} depicts the \emph{magnitude} of the process.

\textbf{FIXME: can you give the respective formula, how you get from the above signal to FA/MD?}
\begin{equation}
FA = \sqrt{ \frac{3}{2}},\frac{\sqrt{ (\lambda_1 - \hat{\lamda})^2 + (\lambda_2 - \hat{\lamda})^2 + (\lambda_3 - \hat{\lamda})^2}}{\sqrt{ {\lambda_1}^2 + {\lambda_2}^2 + {\lambda_3}^2}}
\end{equation}

There exist two main reasons to justify their choice. 
First, they are well-understood and standardized in clinical routine.
Second, together they contain most of the information that is
usually extracted from the \ac{dwi}-derived scalar maps. \\

\subsubsection{Simulated distortions}
